SVG: The Paper

### 2022-05-04 Analysis/index.Rmd
RT v accuracy stuff for clarke2022 qjep

>>>>

## Are more predictable people faster at the task?

```{r}
drt <- filter(d, found == 40) %>% group_by(observer, condition) %>%
  summarise(median_rt = median(RT), .groups = "drop") %>% 
  full_join(dm, by = c("observer", "condition"))

ggplot(drt, aes(accuracy, median_rt, colour = condition)) +
         geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm") -> plt1

ggplot(drt, aes(bP, median_rt, colour = condition)) +
         geom_point(alpha = 0.5) + 
  geom_smooth(method = "lm") -> plt2

plt1 + plt2 + plot_layout(guides = "collect")

summary(lm(median_rt ~ accuracy*condition, data = drt))
summary(lm(median_rt ~ bP*condition, data = drt))
